Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-23 awipev-CO2.Rmd
sal_mix and temp_mix modifications done2

```{r pCO2 2nd cleaning, echo=FALSE, warning=FALSE, message=FALSE}

@@

### **seaFET data cleaning**

```{r seaFET 2nd cleaning, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}

```                
### **seaFET calibration constante E0**

@@

#interpolation of salinity during the FB off maintenance
salinterp <-approx(d_all$datetime, d_all$sal, xout=d_all$datetime, method="linear", rule=2)
names(salinterp) <- c("datetime", "sal_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_interp <- salinterp$sal_interp

d_all$sal <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_interp, d_all$sal)

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_insitu,
                          calT = d_all$temp_insitu, calSal = d_all$sal )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_interp)

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, T_seaF, temp_fb, temp_insitu, sal)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
 # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  dyAxis( "y",valueRange = c(-3, 9))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(Tinsi_max =round( max(temp_insitu, na.rm=TRUE), digits = 2),
            Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
            sal_max = round(max(sal, na.rm=TRUE), digits = 2),
            sal_min = round(min(sal, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
kable(range_month)
```

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal,temp_fb,temp_insitu, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal,temp_fb,temp_insitu, pH_durafet_corrected)%>%
  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

>>>>

@@

### **seaFET calibration constante E0**

@@

#interpolation of salinity during the FB off maintenance
salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
names(salinterp) <- c("datetime", "sal_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_mix_interp <- salinterp$sal_mix_interp

d_all$sal_mix_interp <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_mix_interp, d_all$sal_mix)

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_insitu,
                          calT = d_all$temp_mix, calSal = d_all$sal_mix )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_mix, calSal = d_all$sal_mix_interp)

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, T_seaF, temp_fb, temp_insitu, sal)
# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
#   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
#    # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
# dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
#  # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
#    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
#  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
#   #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
#   #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
#    # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
#   dyLegend(show = "auto")   %>%
#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyAxis( "y",valueRange = c(-3, 9))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)
# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
range_month <-
  d_all %>%
  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
  summarize(Tinsi_max =round( max(temp_mix, na.rm=TRUE), digits = 2),
            Tinsi_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
            sal_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
            sal_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
kable(range_month)
```

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_mix,temp_fb,temp_mix, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_mix), !is.na(temp_fb), !is.na(sal_mix)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_mix, Pinsi=11, S=pH_sf$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal_mix,temp_fb,temp_mix, pH_durafet_corrected)%>%
  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_mix), !is.na(temp_fb), !is.na(sal_mix))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_mix, Pinsi=11, S=pH_dur$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_mix,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal_mix))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
